signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-18 paper.tex
added results from all repetitions

To compare encodings we performed a 5-fold cross-validation training a new instance of signalHsmm on every encoding. We created balanced data sets by subsampling a number of proteins without a signal peptide equal to the number of proteins with signal peptide.
The analysis was carried using also redundant encodings, but results are not shown (HSMM is a deterministic algorithm and predictions for identical groupings of amino acids were the same). The cross-validation was repeated XXX times, to ensure that every negative protein was tested at least once with XXX probability.

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/cvres.png}
\caption{Results of cross-validation. 1. An encoding providing the best sensitivity (AUC = 0.9687, MCC = 0.8689). 2. An encoding providing the best specificity (AUC = 0.9346, MCC = 0.6479).}
\label{fig:cvres}
\end{figure}

@@

>>>>

To compare encodings we performed a 5-fold cross-validation training a new instance of signalHsmm on every encoding. We created balanced data sets by subsampling a number of proteins without a signal peptide equal to the number of proteins with signal peptide.
The analysis was carried using also redundant encodings, but results are not shown (HSMM is a deterministic algorithm and predictions for identical groupings of amino acids were the same). The cross-validation was repeated 60 times. At first, we planned 160 repetitions to ensure with probability 0.95, that every protein without signal peptide was in the learning set, but very small variance of performance measure allowed us to relax this condition.

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/cvres.png}
\caption{Results of cross-validation. 1. The encoding providing the best sensitivity (AUC = 0.9683, MCC = 0.8677). 2. The encoding providing the best specificity (AUC = 0.9338, MCC = 0.6474).}
\label{fig:cvres}
\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrr}
  \toprule
Measure & Mean & SD \\ 
  \midrule
AUC & 0.9683 & 0.0024 \\ 
   \rowcolor[gray]{0.85}MCC & 0.8677 & 0.0049 \\ 
  Sensitivity & 0.9406 & 0.0008 \\ 
   \rowcolor[gray]{0.85}Specificity & 0.9269 & 0.0050 \\ 
   \bottomrule
\end{tabular}
\caption{Performance measures for the best encoding. 60 repetitions of cross-validation.} 
\label{tab:perfmeas}
\end{table}
